Relating games of Menger, countable fan tightness, and selective separability

### 2018-07-06 articles/relating-games-menger-cft-ss/article-zip/article.tex
reorganize article for submission
update zipped article

In dense-separable spaces, it is safe to assume the first player
only chooses countable dense subsets in the \(SS\) and \(CDFT\)
principles/games.

@@

Bella noted that this is certainly true for non-strategic \(SS\),
as verified below. Note the use of knowledge of all \(D_n\) 
to define \(E_n\) in this proof,
demonstrating why it cannot be trivially modified to the \(SS^+\) case.

\begin{proposition}
  Let \(X\) be a dense-separable space such that every countable dense
  subspace \(D\subseteq X\) is \(SS\). Then \(X\) is \(SS\).
\end{proposition}

\begin{proof}
  Take \(\{D_n:n<\omega\}\) with \(D_n\subseteq X\) countable dense,
  so \(E_n=\bigcup\{D_m:n\leq m<\omega\}\) is countable dense in
  the \(SS\) subspace \(D=\bigcup\{D_n:n<\omega\}\). So choose \(F_n\in[E_n]^{<\omega}\)
  with \(cl_D(\bigcup\{F_n:n<\omega\})=D\) and therefore 
  \(cl(\bigcup\{F_n:n<\omega\})=X\).

  Define \(G_n\in[D_n]^{<\omega}\) by \(G_n=D_n\cap\bigcup\{F_m:m\leq n\}\).
  The result follows as \(\bigcup\{G_n:n<\omega\}=\bigcup\{F_n:n<\omega\}\).
\end{proof}

@@

\begin{theorem}
  A topological space is \(M^+\) if and only if it is \(\Omega M^+\).
\end{theorem}

@@

\section{Acknowledgements}
The author would like to thank Ziqin Feng and Gary Gruenhage
for their helpful comments on the topic of \(C_p(\onePtLind{\omega_1})\).
The author also thanks the anonymous referree who pointed out
the game strategies in Proposition \ref{cofinalSequence} could handle all
subsequences rather than only final sequences, in addition to the
observation given as the final result of the third section.

\bibliographystyle{plain}
\bibliography{../../bibliography}

>>>>

As noted earlier, all \(SS\) spaces are separable as witnessed
by choosing \(D_n=X\); in fact, they
are dense-separable as witnessed by choosing \(D_n=D\) for
any dense subset \(D\) of \(X\).
As such, it is safe to assume that the first player
only chooses countable dense subsets in the \(SS\) and \(CDFT\)
principles/games.

@@

Bella noted that this is certainly true for non-strategic \(SS\),
as shown below.
Note that the knowledge of all \(D_n\) is used to define \(D\)
in this proof, preventing a trivial modification to answer the
above question.

\begin{proposition}\label{ds-ss}
  Let \(X\) be a dense-separable space such that every countable dense
  subspace \(D\subseteq X\) is \(SS\). Then \(X\) is \(SS\).
\end{proposition}

\begin{proof}
  Take \(\{D_n:n<\omega\}\) with \(D_n\subseteq X\) countable dense in
  \(X\), and therefore countable dense in the \(SS\) subspace 
  \(D=\bigcup\{D_n:n<\omega\}\),
  So choose \(E_n\in[D_n]^{<\omega}\)
  with \(cl_D(\bigcup\{E_n:n<\omega\})=D\) and therefore 
  \(cl(\bigcup\{E_n:n<\omega\})\supseteq cl(D)=X\). Thus the \(E_n\)
  witness that \(X\) is \(SS\). 
\end{proof}

@@

\begin{theorem}\label{m-om}
  A topological space is \(M^+\) if and only if it is \(\Omega M^+\).
\end{theorem}

@@

\section{Acknowledgements}
The author would like to thank Ziqin Feng and Gary Gruenhage
for their helpful comments on the topic of \(C_p(\onePtLind{\omega_1})\).
The author also thanks the anonymous referee for their helpful suggestions
to improve Propositions \ref{cofinalSequence} and \ref{ds-ss}, and the observation
of Theorem \ref{m-om}.

\bibliographystyle{plain}
\bibliography{bibliography}
